---
title: "DV2_Homework"
author: '2000692'
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---


```{r setup, include=FALSE}
## Global options
library(knitr)
opts_chunk$set(include = T, message = F, warning = F, cache = T)
rm(list = ls())

# load packages
library(rmdformats)
library(nycflights13)
library(data.table)
library(ggplot2)
library(dplyr)
library(GGally)
library(psych)
library(readxl)
library(ggrepel)
theme_set(theme_light()) 
```

## 0. Load the nycflights13 package and check what kind of datasets exist in the package, then create a copy of flights dataset into a data.table object, called flight_data.
```{r}
data(package ="nycflights13")$results[,c("Item", "Title")]
flight_data <- data.table(nycflights13::flights)
```

## 1. Which destination had the lowest avg arrival delay from LGA with minimum 100 flight to that destination?
```{r}
flight_data[origin== "LGA", list(number_of_flights = .N,
                                 mean_arr_delay= mean(arr_delay,na.rm = T)),
            by= dest][number_of_flights >= 100][order(mean_arr_delay)][1]
```
Or a second method:
```{r}
flight_data %>% 
  filter(origin == 'LGA') %>% 
  group_by(dest) %>% 
  summarise(n = n(), mean_arr_delay = mean(arr_delay, na.rm=T) ) %>% 
  filter(n >=100)%>% 
  arrange(mean_arr_delay) %>% 
  head(1)
```

## 2. Which destination's flights were the most on time (avg arrival delay closest to zero) from LGA with minimum 100 flight to that destination?
```{r}
flight_data[origin== "LGA", list(number_of_flights = .N,
                                 mean_arr_delay= abs(mean(arr_delay,na.rm = T))),
            by= dest][number_of_flights >= 100][order(mean_arr_delay)][1]
```

## 3. Who is the manufacturer of the plane, which flights the most to CHS destination?
```{r}
planes <- data.table(nycflights13::planes)

merge(planes,
  flight_data[dest== "CHS",  .(number_of_flights=.N), by = tailnum],
  by = 'tailnum')[, list(tailnum,number_of_flights,manufacturer)][order(-number_of_flights)][1]
```
Or a second method:
```{r}
merge(flight_data,planes, by="tailnum")[dest == "CHS",list(number_of_flights = .N,
                                                           manufacturer), 
           by= tailnum][order(-number_of_flights)][1]
```

## 4. Which airline (carrier) flow the most by distance?
```{r}
carrier_data <- nycflights13::airlines

merge(flight_data,carrier_data, by="carrier")[, list(sum_of_distance= sum(distance)),
by= name][order(-sum_of_distance)][1]
```

## 5. Plot the monthly number of flights with 20+ mins arrival delay!
```{r}
flight_data[arr_delay > 20, list(number_of_flights = .N), by = month] %>% 
  ggplot(aes(x= month, y=number_of_flights)) +
  geom_col() +
  labs(x="Month", y= "Number of Flights") +
  scale_x_continuous(breaks=seq(1, 12, by = 2),
                     labels = c(paste0(month.abb[seq(1, 12, by = 2)], " 2013")))
```

## 6. Plot the departure delay of flights going to IAH and the related day's wind speed on a scaterplot! Is there any association between the two variables? Try adding a linear model.
```{r}
weather <- data.table(nycflights13::weather)

merge(weather[, .(mean_ws=mean(wind_speed)), by = list(year, month, day, origin)],
  flight_data[dest== "IAH",  .(dep_delay,origin), by = list(year, month, day)],
  by = c('year', 'month', 'day', 'origin')) %>% 
ggplot(aes(x= dep_delay,y=mean_ws))+
  geom_point() +
  geom_smooth(method = 'lm')+
  labs(x="Departure Delay",y="Mean of Wind Speed")
  
```

## 7. Plot the airports as per their geolocation on a world map, by mapping the number flights going to that destionation to the size of the symbol!

```{r fig.width=9,fig.height=5}
airport_data <- data.table(airports)

merge(airport_data[,list(faa,lat,lon)],
      flight_data, 
      by.x="faa", by.y="dest")[, .(lon, lat,flights=.N), by = faa] %>% 
  ggplot(aes(lon, lat, size = flights)) +
  borders("world") +
  geom_point() +
  coord_quickmap()+
  theme(legend.position="top")
```
Or a second method:
```{r fig.width=9,fig.height=5}
  flight_data %>%
  group_by(dest) %>% 
  summarise(flights = n()) %>%
  inner_join(airports, by = c(dest = "faa"))%>%
  ggplot(aes(lon, lat, size = flights)) +
  borders("world") +
  geom_point() +
  coord_quickmap()+
  theme(legend.position="top")
```
